---
title: "Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include = FALSE}
library(WebGestaltR)
```

---

### Requirements

- Rust 1.66.0 or later
- R 4.0.0 or later (Windows requires 4.2+)

---

Since WebGestaltR v1.0.0, Rust is used for core computations in the R package. Therefore, to install WebGestaltR, please download and install Rust from [https://www.rust-lang.org/tools/install](https://www.rust-lang.org/tools/install). For Mac, Linux, or Unix users, Rust can be installed from the command line, and Windows users can download a GUI installer.

Restart your terminal after installing Rust to ensure the Rust compiler is available in your path. You can check that Rust is installed correctly by running `rustc --version` in your terminal.

After installing Rust, you can install WebGestaltR by running the following command in an R session:

```R
# install.packages("devtools") # run if devtools not already installed
devtools::install_github("iblacksand/WebGestaltR")
```

During installation, the Rust compiler will be called to build the computation library used by WebGestaltR. If you run into problems with installation of the new version, please [open a new issue](https://github.com/iblacksand/WebGestaltR/issues/new?assignees=iblacksand&labels=Installation&projects=&template=installation-issue.md&title=).
